Inattentive responding can induce spurious associations between task behavior and symptom measures

### 2023-06-21 manuscripts/main.tex
minor fixes

% \subsection*{Screening for C/IE responding is common for task behavior but not for self-report surveys}
\subsection*{Narrative review of task and self-report screening practices}

@@

Among studies that we reviewed, approximately 80\% (39/49) used at least one method to identify C/IE responding in task behavior (Table \ref{tab:tab01}). Of these, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies. Most common (46\% of all studies) was identifying participants whose performance was statistically indistinguishable from chance-level on some measure of accuracy. Almost as common (38\%) was screening based on low response variability (i.e., excluding participants who predominantly responded in the same fashion across trials, such as using only a single response key).

@@

% \subsection*{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
\subsection*{C/IE participants appear psychiatric when symptoms are rare}

@@

% \subsection*{Low correspondence between task and self-report measures of C/IE responding}
\subsection*{Low agreement between task and self-report screening measures}

@@

% \subsection*{Spurious symptom-behavior correlations produced by C/IE responding}
\subsection*{C/IE responding yields spurious symptom-behavior correlations}

@@

% \subsection*{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}
\subsection*{Findings replicate in second study with alternative measures}

@@

% \subsection*{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
\subsection*{Patients with depression do not fail attention checks more often}

>>>>

\subsection*{Narrative review of task and self-report screening practices}

@@

Among studies that we reviewed, approximately 80\% (39/49) used at least one method to identify C/IE responding in task behavior (Table \ref{tab:tab01}). Of these, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies. Most common (46\% of these studies) was identifying participants whose performance was statistically indistinguishable from chance-level on some measure of accuracy. Almost as common (38\% of these studies) was screening based on low response variability (i.e., excluding participants who predominantly responded in the same fashion across trials, such as using only a single response key).

@@

\subsection*{C/IE participants appear psychiatric when symptoms are rare}

@@

\subsection*{Low agreement between task and self-report screening measures}

@@

\subsection*{C/IE responding yields spurious symptom-behavior correlations}

@@

\subsection*{Findings replicate in second study with alternative measures}

@@

\subsection*{Patients with depression do not fail attention checks more often}
